---
title: "HW3"
output: github_document
---

## Problem 1 Solution

#### Importing data
```{r}
library(p8105.datasets)
data("instacart")

tail(instacart)
```

This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` variables. The variables include `r colnames(instacart)`. These variables record unique numeric identifiers like ID about user and product, and descriptive character observations about name and category.

#### a.
```{r}
library(tidyverse)
instacart %>%
  count(aisle) %>%
  arrange(desc(n))
```

There are `r length(unique(pull(instacart, aisle)))` aisles. _fresh vegetables_, _fresh fruits_ and _packaged vegetables fruits_ are the most items ordered from, all of which have more than **78000** observations.

#### b.
```{r}
library(ggridges)
instacart %>%
  count(aisle) %>%
  filter(n > 10000) %>%
  ggplot(aes(x = aisle, y = n)) + geom_point() + theme(axis.text.x = element_text
  (angle = 90)) +
  labs(
    title = "The number of items ordered in each aisle",
    x = "Aisles",
    y = "Items Ordered"
  )
```

#### c.
```{r}
instacart %>% 
    filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
    group_by(aisle) %>% 
    count(product_name) %>% 
    mutate(rank = min_rank(desc(n))) %>% 
    filter(rank <= 3) %>% 
    arrange(aisle, rank) %>% 
    knitr::kable()
```


#### d.
```{r}
instacart %>% 
  filter(product_name == "Pink Lady Apples" | product_name ==  "Coffee Ice Cream") %>%
  group_by(product_name, order_dow) %>% 
  summarize(
   mean_hour = mean(order_hour_of_day)
  ) %>% 
   mutate(
     order_dow = recode(order_dow, "0" = "Sun", "1" = "Mon", "2" = "Tue", "3" = "Wed", "4" = "Thu", "5" = "Fri", "6" = "Sat"),
     mean_hour = round(mean_hour, 2)
     ) %>% 
    pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  ) %>% 
   knitr::kable()
```

## Problem 2 Solution

```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```
